---
title: "fable::ISF2019"
subtitle: "Flexible futures for fable functionality"
author: "Mitchell O'Hara-Wild"
date: '12/05/2019'
output:
  xaringan::moon_reader:
    chakra: ./libs/remark-latest.min.js
    css: ["./libs/slides.css",  "./libs/animate.css"]
    lib_dir: ./libs
    seal: false
    nature:
      highlightStyle: github
      ratio: '16:9'
      highlightLines: true
      countIncrementalSlides: false
      beforeInit: ["./libs/jquery/jquery.min.js", "./libs/slides.js"]
---
class: inverse

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE, width = 120)

library(tidyverse)
library(knitr)
library(kableExtra)
library(fontawesome)
library(lubridate)
library(htmltools)

library(tsibble)
library(fasster)
library(fable)

opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center',
  fig.width = 12, fig.height = 4, fig.show = 'hold',
  cache = TRUE, external = TRUE, dev = 'svglite', dev.args = list(bg = "transparent")
)

mp4_vid <- function(src){
  HTML(
    paste0(
      '<video autoplay>
        <source src="', src, '" type="video/mp4">
      </video>'
    )
  )
}

hook_output <- knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
   lines <- options$output.lines
   if (is.null(lines)) {
     return(hook_output(x, options))  # pass to default hook
   }
   x <- unlist(strsplit(x, "\n"))
   more <- "..."
   if (length(lines)==1) {        # first n lines
     if (length(x) > lines) {
       # truncate the output, but add ....
       x <- c(head(x, lines), more)
     }
   } else {
     x <- c(more, x[lines], more)
   }
   # paste these lines together
   x <- paste(c(x, ""), collapse = "\n")
   hook_output(x, options)
 })

theme_set(
  theme_grey(base_size = 16) +
  theme(
    legend.position = "bottom",
    plot.background = element_rect(fill = "transparent"),
    legend.background = element_rect(fill = "transparent")
  )
)
```


```{css, echo=FALSE}
/* custom.css */
.left-code {
  color: #777;
  width: 40%;
  height: 92%;
  float: left;
}
.right-plot {
  width: 58%;
  float: right;
  padding-left: 1%;
}
```


.title[fable]
.sticker-float[![fable](resources/fable.svg)]

## Flexible futures for fable functionality

.bottom[
### Mitchell O'Hara-Wild (`r fa("twitter", fill="#1da1f2")`[@mitchoharawild](https://twitter.com/mitchoharawild))
### Rob Hyndman (`r fa("twitter", fill="#1da1f2")`[@robjhyndman](https://twitter.com/robjhyndman/))
### 19 June 2019
### Slides @ [slides.mitchelloharawild.com/isf2019](https://slides.mitchelloharawild.com/isf2019)
]

---
class: center

.animated.fadeIn[
## Forecasting in the tidyverse

.sticker[![fable](resources/fable.svg)]

]


---
class: center

## Forecasting in the tidyverse

.sticker[![fable](resources/fable.svg)]

.animated.fadeIn[
.sticker[![tsibbledata](resources/tsibbledata.svg)]
.sticker[![feasts](resources/feasts.svg)]
.sticker[![tsibble](resources/tsibble.svg)]
]

---

class: top

.sticker-float[![tsibble](resources/tsibble.svg)]

# Tidy temporal data structure

### Domestic tourism in Australia

```{r tourism-data, echo = TRUE}
library(tsibble)
tourism
```

---

class: top

.sticker-float[![feasts](resources/feasts.svg)]

# A peak at the features

### Compute features relating to STL decompositions

```{r tourism-features, echo = TRUE}
library(feasts)
tourism_features <- tourism %>% 
  features(Trips, feature_set(tags = "stl"))
```

```{r tourism-features-print, echo = FALSE}
tourism_features
```

---

class: top

.sticker-float[![ggplot2](resources/ggplot2.svg)]

# A peak at the features

.full-width[
```{r tourism-features-plot, echo = TRUE}
library(ggplot2)
tourism_features %>% 
  ggplot(aes(x = trend_strength, y = seasonal_strength_year, colour = Purpose)) + 
  geom_point() + stat_density_2d(aes(fill = Purpose, alpha = ..level..), bins = 5, geom = "polygon") + 
  facet_wrap(vars(Purpose), nrow = 1) + coord_equal() + xlim(c(0,1)) + ylim(c(0,1))
```
]

---

class: top

.sticker-float[![tsibble](resources/tsibble.svg)].sticker-float[![dplyr](resources/dplyr.svg)]

# Total holidays across Australia

### Starting from the top

```{r tourism-total, echo = TRUE, fig.show='hide'}
library(dplyr)
holiday_aus <- tourism %>% 
  filter(Purpose == "Holiday") %>% 
  summarise(Trips = sum(Trips))

holiday_aus %>% 
  autoplot(Trips)
```

.flex-row[
```{r tourism-total-print, echo = FALSE}
holiday_aus
```
.full-width[
```{r tourism-total-plot, echo = FALSE}
holiday_aus %>% 
  autoplot(Trips)
```
]
]

---

class: top

.sticker-float[![fable](resources/fable.svg)]

# Forecasting with fable

### Look at the data

<br>

.left-code[
```{r tourism-total-ets-data, eval=FALSE, echo=TRUE}
holiday_aus #<<
```
]
.right-plot[
```{r tourism-total-ets-data-output, ref.label="tourism-total-ets-data", echo=FALSE, cache=TRUE, fig.height = 6}
```
]

---

class: top

.sticker-float[![fable](resources/fable.svg)]

# Forecasting with fable

### Specify and estimate a model

<br>

.left-code[
```{r tourism-total-ets-model, eval=FALSE, echo=TRUE}
holiday_aus %>% 
  model(ETS(Trips)) #<<
```
]
.right-plot[
```{r tourism-total-ets-model-output, ref.label="tourism-total-ets-model", echo=FALSE, cache=TRUE, fig.height = 6}
```
]

---

class: top

.sticker-float[![fable](resources/fable.svg)]

# Forecasting with fable

### Make some forecasts

<br>

.left-code[
```{r tourism-total-ets-forecast, eval=FALSE, echo=TRUE}
holiday_aus %>% 
  model(ETS(Trips)) %>% 
  forecast(h = "3 years") #<<
```
]
.right-plot[
```{r tourism-total-ets-forecast-output, ref.label="tourism-total-ets-forecast", echo=FALSE, cache=TRUE, fig.height = 6}
```
]

---

class: top

.sticker-float[![fable](resources/fable.svg)]

# Forecasting with fable

### See the results!

<br>

.left-code[
```{r tourism-total-ets-plot, eval=FALSE, echo=TRUE}
holiday_aus %>% 
  model(ETS(Trips)) %>% 
  forecast(h = "3 years") %>% 
  autoplot(holiday_aus) #<<
```
]
.right-plot[
```{r tourism-total-ets-plot-output, ref.label="tourism-total-ets-plot", echo=FALSE, cache=TRUE, fig.height = 6}
```
]


---

class: top, inverse

.sticker-float[![fable](resources/fable.svg)]

<br>

## It's easy to make forecasts...

<br>

# But are they good forecasts?

---
class: top

.sticker-float[![fable](resources/fable.svg)]

# Forecast accuracy evaluation


- Trai

### Measures

---
class: top

.sticker-float[![fable](resources/fable.svg)]

# Comparing multiple models

### Estimate multiple models

<br>
.left-code[
```{r tourism-total-many-mdls, eval=FALSE, echo=TRUE}
holiday_aus %>% 
  model(
    ets_n = ETS(Trips ~ trend("N")), #<<
    ets_a = ETS(Trips ~ trend("A")), #<<
    arima = ARIMA(Trips) #<<
  )
```
]
.right-plot[
```{r tourism-total-many-mdls-output, ref.label="tourism-total-many-mdls", echo=FALSE, cache=TRUE, fig.height = 6}
```
]

---

class: top

.sticker-float[![fable](resources/fable.svg)]

# Comparing multiple models

### Forecasts from multiple models

<br>
.left-code[
```{r tourism-total-many-plot, eval=FALSE, echo=TRUE}
holiday_aus %>% 
  model(
    ets_n = ETS(Trips ~ trend("N")),
    ets_a = ETS(Trips ~ trend("A")),
    arima = ARIMA(Trips)
  ) %>% 
  forecast(h = "3 years") %>% #<<
  autoplot(holiday_aus, level = NULL) #<<
```
]
.right-plot[
```{r tourism-total-many-plot-output, ref.label="tourism-total-many-plot", echo=FALSE, cache=TRUE, fig.height = 6}
```
]


---

class: top

.sticker-float[![fable](resources/fable.svg)]

# Comparing multiple models

### Compare model performance

<br>
.left-code[
```{r tourism-total-many-acc, eval=FALSE, echo=TRUE}
holiday_aus %>% 
  model(
    ets_n = ETS(Trips ~ trend("N")),
    ets_a = ETS(Trips ~ trend("A")),
    arima = ARIMA(Trips)
  ) %>% 
  accuracy() %>% #<<
  arrange(MASE) #<<
```
]
.right-plot[
```{r tourism-total-many-acc-output, ref.label="tourism-total-many-acc", echo=FALSE, cache=TRUE, fig.height = 6}
```
]

---
class: inverse, top

.sticker-float[![fable](resources/fable.svg)]

# Model ensembling

### Is the combination better than its parts?

---

class: top

.sticker-float[![fable](resources/fable.svg)]

# Model ensembling

### A simple average of forecasts

<br>
.left-code[
```{r tourism-total-combn, eval=FALSE, echo=TRUE}
holiday_aus %>% 
  model(
    ets_n = ETS(Trips ~ trend("N")),
    ets_a = ETS(Trips ~ trend("A")),
    arima = ARIMA(Trips)
  ) %>% 
  mutate(
    combn = (ets_n + ets_a + arima)/3 #<<
  )
```
]
.right-plot[
```{r tourism-total-combn-output, ref.label="tourism-total-combn", echo=FALSE, cache=TRUE, fig.height = 6}
```
]

---

class: top

.sticker-float[![fable](resources/fable.svg)]

# Model ensembling

### Is the combination better than its parts?

<br>
.left-code[
```{r tourism-total-combn-acc, eval=FALSE, echo=TRUE}
holiday_aus %>% 
  model(
    ets_n = ETS(Trips ~ trend("N")),
    ets_a = ETS(Trips ~ trend("A")),
    arima = ARIMA(Trips)
  ) %>% 
  mutate(
    combn = (ets_n + ets_a + arima)/3
  ) %>% 
  accuracy() %>% #<<
  arrange(MASE) #<<
```
]
.right-plot[
```{r tourism-total-combn-acc-output, ref.label="tourism-total-combn-acc", echo=FALSE, cache=TRUE, fig.height = 6}
```
]

---

class: top

.sticker-float[![fable](resources/fable.svg)]

# Model ensembling

### Is the combination better than its parts?

<br>
.left-code[
```{r tourism-total-combn-fc, eval=FALSE, echo=TRUE}
holiday_aus %>% 
  model(
    ets_n = ETS(Trips ~ trend("N")),
    ets_a = ETS(Trips ~ trend("A")),
    arima = ARIMA(Trips)
  ) %>% 
  mutate(
    combn = (ets_n + ets_a + arima)/3
  ) %>% 
  select(combn) %>% #<<
  forecast(h = "3 years") #<<
```
]
.right-plot[
```{r tourism-total-combn-fc-output, ref.label="tourism-total-combn-fc", echo=FALSE, cache=TRUE, fig.height = 6}
```
]

---

class: top

.sticker-float[![fable](resources/fable.svg)]

# Model ensembling

### Is the combination better than its parts?

<br>
.left-code[
```{r tourism-total-combn-plot, eval=FALSE, echo=TRUE}
holiday_aus %>% 
  model(
    ets_n = ETS(Trips ~ season("A")),
    ets_a = ETS(Trips ~ season("M")),
    arima = ARIMA(Trips)
  ) %>% 
  mutate(
    combn = (ets_n + ets_a + arima)/3
  ) %>% 
  select(combn) %>% 
  forecast(h = "3 years") %>% 
  autoplot(holiday_aus) #<<
```
]
.right-plot[
```{r tourism-total-combn-plot-output, ref.label="tourism-total-combn-plot", echo=FALSE, cache=TRUE, fig.height = 6}
```
]

---

# Inconclusive for just one series

### We should scale it up

```{r tourism-data-2, echo = TRUE}
tourism
```

---

# But wait, there's more

### We can also model the aggregations

```{r tourism-agg, echo = TRUE}
tourism_agg <- tourism %>% 
  aggregate_key((State / Region) * Purpose, Trips = sum(Trips))
```

```{r tourism-agg-print, echo = FALSE}
tourism_agg
```

---

# This may take a while

### Good think it can be done in parallel!

```{r tourism-agg-mdl, echo = TRUE, cache = TRUE}
library(future)
plan(multiprocess)
fit <- tourism_agg %>% 
  filter(Quarter < yearquarter("2015 Q1")) %>% 
  model(
    ets_n = ETS(Trips ~ trend("N")),
    ets_a = ETS(Trips ~ trend("A")),
    arima = ARIMA(Trips)
  ) %>% 
  mutate(
    combn = (ets_n + ets_a + arima)/3
  )
```
```{r tourism-agg-mdl-print, echo = FALSE}
fit
```


---

# Are the combinations better?

### Let's find out...

```{r tourism-agg-acc, echo = TRUE, cache = TRUE}
tourism_accuracy <- accuracy(fit)
tourism_accuracy
```

---

# Are the combinations better?

### Let's find out...

```{r tourism-agg-acc-central, echo = TRUE, cache = TRUE}
tourism_accuracy %>% 
  group_by(.model) %>%
  summarise(mean(MASE), median(MASE)) %>% 
  arrange(`median(MASE)`)
```

---

# Are the combinations better?

### Let's find out...

```{r tourism-agg-acc-plot, echo = TRUE, cache = TRUE}
tourism_accuracy %>% 
  ggplot(aes(x = MASE, colour = .model)) +
  geom_density() + scale_x_log10()
```

---

class: inverse, top

.sticker-float[![fable](resources/fable.svg)]

.title[Thanks! `r fa("comments", fill = "white")`]

<br>

.larger[
`r fa("github", fill = "white")` Learn more on GitHub: [tidyverts/fable](https://github.com/tidyverts/fable)

`r fa("chart-line", fill = "white")` Keep updated: [tidyverts.org](http://www.tidyverts.org)

`r fa("desktop", fill = "white")` Review slides: [slides.mitchelloharawild.com/isf2019](https://slides.mitchelloharawild.com/isf2019)

<br>

.footnote[This work is licensed as `r fa("creative-commons", fill="white")` BY-NC 4.0.]
]
